### 2016-08-23 number_theory/defs.tex
starting new semester

\newcommand{\Define}[1]{\item\underline{#1}:}
\newcommand{\prm}{p}

@@

\begin{enumerate}
\Define{Prime Number} A positive $n\in\ZZ$ such that $n>1$ is prime if its only
divisors are 1 and $n$.

\Define{Fundamental Theorem of Arithmetic} Suppose $n\in\ZZ > 1$. Then
\begin{enumerate}
\item $\exists\alpha_{1},\alpha_{2},\dots,\alpha_{n}\in\NN$ and primes $\prm_{1},
\prm_{2},\dots,\prm_{n}$ such that $n=\prm_{1}^{\alpha_{1}}\prm_{2}^{\alpha_{2}}
\dots\prm_{n}^{\alpha_{n}}$, or $n=\prod_{i=1}^{n}\prm_{i}^{\alpha_{i}}$.
\item The expression $\prod_{i=1}^{n}\prm_{i}^{\alpha_{i}}$ is unique up to
permutation of the primes.

\Define{Lemma} Suppose $\prm$ is prime and $a,b\in\ZZ$.
\begin{enumerate}
\item If $\prm\nmid a$, then $\prm$ and $a$ are relatively prime.
\item If $\prm\mid ab$, then $\prm\mid a$ xor $\prm\mid b$.
\end{enumerate}

\Define{Corollary} If $\prm$ is prime and divides $a_{1},a_{2},\dots,a_{n}$, then
$p|a_{i}$ for some $i\in\{ 1,2,\dots,n \}$.

\Define{Corollary} If $m$ is not a perfect square, then $\sqrt{m}\notin\QQ$.
\end{enumerate}

\Define{Exact Division} If $\prm^{\alpha}\mid n$ and $\prm^{\alpha+1}\nmid n$, then
$\prm^{\alpha}$ exactly divides $n$, noted as $\prm^{\alpha}||n$.

\Define{Theorem} Suppose $a_{1},a_{2},\dots,a_{k}$ are pairwise relatively prime
and are greater than 0. If $a_{1}a_{2}\dots a_{k} = x^{m}$ for some $x\in\NN$ and
$m\geq2$, then $\exists x_{i}\in\NN$ such that $a_{i} = x_{i}^{m}$ for all $i$.

\Define{Theorem} There are infinitely many primes.

\Define{Prime Number Theorem} Let $\pi(x)$ denote the number of primes such that
$\prm_{i}\leq x$. We have that
\begin{enumerate}
\item $\lim_{x\to\infty}\pi(x)=\infty$
\item $\pi(x) < x$ for $x\geq2$.
\end{enumerate}
We can also define the logarithmic integral as
$\mathcal{L}_{i}(x)=\int_{2}^{x}{1\over\log{t}}\mathop{dt}$. Then
\[
\lim_{x\to\infty}{\mathcal{L}_{i}\over\pi(x)}=
\lim_{x\to\infty}{{x\over\log{x}}\over\pi(x)} = 1
\]
\end{enumerate}
\end{document}

>>>>

\newcommand{\Define}[1]{\item\underline{#1}:}
\newcommand{\prm}{p}
\newcommand{\set}[1]{\mathcal{#1}}
\newcommand{\setA}{\mathcal{A}}
\newcommand{\setB}{\mathcal{B}}
\newcommand{\setU}{\set{U}}

@@

\section{Definitions}

\subsection{Sets and Logic}
\begin{enumerate}
\Define{Logical Operator} A logical operator is a symbol that acts on a logical statement. The operators act as follows
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
& & Negation & Disjunction & Conjunction & Implication\\
\hline
P & Q & $\neg$ P & P $\wedge$ Q & P $\vee$ Q & P $\implies$ Q \\
\hline
1 & 1 & 0 & 1 & 1 & 1\\
1 & 0 & 0 & 0 & 1 & 0\\
0 & 1 & 1 & 0 & 1 & 1\\
0 & 0 & 1 & 0 & 0 & 1\\
\hline
\end{tabular}
\end{center}
A statement that is always true (i.e. P $\vee\ \neg$P) is called a Tautology. A statement that is always false (i.e. P $\wedge\ \neg$P) is called a contradiction.\\
An implication P $\implies$ Q is made of two parts: the hypothesis (P) and the conclusion (Q).\\
Additionally, statements can be quantified using the two quantifiers, the universal quantifier, for all ($\forall$) and the existential quantifier, there exists ($\exists$).
\Define{Set} A set is a collection of objects. The objects in a set are called elements.
\Define{Empty Set} The empty set, symbolized by $\emptyset$ is the set with no elements.
\Define{Subset} A set $\setA$ is a subset of a set $\setB$ (noted $\setA\subset\setB$) if for all $x\in\setA$, $x\in\setB$.
\Define{Power Set} The power set of a set $\setA$ (noted $\set{P}(\setA)$) is the set of all subsets of $\setA$.
\Define{The Universal Set} The universal set, $\setU$ is the set of which all sets are subsets.
\Define{Intersection} For sets $\setA$ and $\setB$, the intersection ($\setA\cap\setB$) is the set of elements in both $\setA$ and $\setB$.
\[\setA\cap\setB = \{x|x\in\setA\wedge x\in\setB\}.\]
To say that $\setA$ and $\setB$ have a trivial intersection means that $\setA\cap\setB=\emptyset$. This is equivalent to saying $\setA$ and $\setB$ are disjoint.
\Define{Union} For sets $\setA$ and $\setB$, the union ($\setA\cup\setB$) is the set of elements in either $\setA$ or $\setB$.
\[\setA\cup\setB = \{x|x\in\setA\vee x\in\setB\}.\]
\Define{Set Difference} The set difference of a set $\setA$ and a set $\setB$ ($\setA-\setB$) is the set of all elements in $\setA$ that are not in $\setB$.
\[\setA-\setB=\{x|x\in\setA\wedge x\notin\setB\}.\]
The complement of a set $\setA$ in regards to $\setU$ is $\setU-\setA$.
\Define{Cartesian Product} For sets $\setA$ and $\setB$, the cartesian product ($\setA\times\setB$) is defined to be the set of ordered pairs $(a,b)$ such that $a\in\setA$ and $b\in\setB$.
\[\setA\times\setB=\{(a,b)|a\in\setA\wedge b\in\setB\}.\]
\Define{Axiom} An axiom is a statement whose truth value is accepted without proof.
\Define{Theorem} A theorem is a mathematical statement whose truth value can be verified through proof.
\Define{Lemma} A Lemma is a mathematical result that is used to prove other results.
\Define{Corollary} A corollary is a mathematical result that follows from another result.
\end{enumerate}

\newpage
\subsection{Number Theory}
\begin{enumerate}
\Define{Division} To say that $a$ divides $b$ ($a\mid b$) implies that $\exists x\in\ZZ$ such that $b=ax$.
\Define{Relation} A relation $\mathcal{R}$ from $\setA$ to $\setB$ is a subset of $\setA\times\setB$.
$\setA$ is related to $\setB$ ($a\mathcal{R}b$) if $(a,b)\in\mathcal{R}$ for all $a\in\setA$ and
$b\in\setB$. The domain of $\mathcal{R}$ is the set $\{x\ |\ (x,y)\in\mathcal{R}\}$. The range of
$\mathcal{R}$ is the set $\{y\ |\ (x,y)\in\mathcal{R}\}$. If $\mathcal{R}$ has an inverse
$\mathcal{R}^{-1}$, then it is $\{(y,x)\ |\ (x,y)\in\mathcal{R}\}$. A relation between two elements
$a\in\setA$ and $b\in\setB$ is denoted by $a\sim b$.
\Define{Reflexive} A relation $\mathcal{R}$ is reflexive if $x\mathcal{R}x$ for all $x\in\setA$.
\Define{Symmetric} A relation $\mathcal{R}$ is symmetric if $x\mathcal{R}y$ and $y\mathcal{R}x$ for all
$x\in\setA$ and $y\in\setB$.
\Define{Transitive} A relation $\mathcal{R}$ is transitive if $x\mathcal{R}y$ and $y\mathcal{R}z$ implies
$x\mathcal{R}z$ for all $x\in\setA$, $y\in\setB$, and $z\in\set{C}$.
\Define{Equivalence Relation} An equivalence relation is a relation that is reflexive, symmetric, and
transitive.
\Define{Equivalence Class} For a non-empty set $\setA$ containing elements $a$ and $b$, the equivalence
class of $a$, noted $[a]$ is the set $\{b\ |\ b\sim a\}$.
\Define{Partition} A partition of a non-empty set $\setA$ is the set of subsets where
\begin{enumerate}
\item The union of all sets in the partition of $\setA$ is $\setA$
\item The intersection of any two different sets in the partition of $\setA$ is not equivalent to
$\emptyset$.
\end{enumerate}
\Define{Function} A function $f$ from $\setA\to\setB$ is a relation from $\setA$ to $\setB$ that satisfies
\begin{enumerate}
\item $(a,b)\wedge(a,c)\in f\implies b=c$.
\item $\forall a\in\setA, \exists b\in\setB$ such that $(a,b)\in f$.
\end{enumerate}
\Define{Image} The image of a function $f:\setA\to\setB$ is $\{f(a)\ |\ a\in\setA\}$.
\Define{Inverse Image} For a function $f:\setA\to\setB$ and sets $\setB$ and $\set{D}$ where
$\set{D}\subset\setB$, the inverse image of $\set{D}$, $f^{-1}(\set{D})$, is defined to be
$\{a\in\setA\ |\ f(a)\in\set{D}\}$.
\Define{Injection} A function $f$ is injective if $\forall (a,b)\in\set{X},\ f(a)=f(b)\implies a=b$.
\Define{Surjection} A function $f$ is surjective if $\forall y\in\set{Y},\ \exists x\in\set{X}$ such that
$f(x)=y$.
\Define{Bijection} A function $f$ is a bijection if it is an injection and a surjection.
\end{enumerate}

\newpage
\section{Theorems and Important Ideas}
\begin{enumerate}
\Define{Division Algorithm} Suppose $a,b\in\ZZ$ and assume $b>0$. Then $\exists q,r\in\ZZ$ such that
$a=qb+r$ and $0\leq r\leq b$. Moreover, $q$ and $r$ are the only integers satisfying this property.
The integer $q$ is commonly called the quotient and $r$ is commonly called the remainder.
\begin{quote}
\textit{\textbf{Proof}}: Let $\set{S}=\{a-nb\ |\ n\in\ZZ\}$. We know that
\[
\lim_{n\to-\infty}(a-nb)\to+\infty,
\]
so $\set{S}$ must contain at least one positive integer. Let $r$ be the smallest element of $\set{S}$
that is greater than zero, called the remainder. Then there is a $q\in\ZZ$ such that $r=a-qb\geq0$, or
$a=qb+r$ for $r\geq0$. We have shown that this $r$ exists.\\
Assume $r\geq b$. Then $r-b\geq0$, and we know $r=a-qb$, so $a-qb-b\geq 0$. Then $a-b(q+1)\in\set{S}$
is greater than zero but less than $r$, which is a contradiction since $r$ is the smallest positive
integer in $\set{S}$. Therefore $a=qr+b$ and $0\leq r\leq b$.\\
Assume $a=bq+r$ and $a=bg+h$ where $0\leq r\leq b$ and $0\leq h\leq g$.
\end{quote}
\end{enumerate}
\end{document}

### 2016-08-23 pde_two/threshold.tex
starting new semester

\subsection{Analysis of the Initial Conditions}
We begin by letting
\[
F(t)=\int_{0}^{\pi}u(x,t)\sin{x}\dx.
\]
Differentiating with respect to $t$ yields
\begin{align*}
F'(t)&=\int_{0}^{\pi}u_{t}\sin{x}\dx\\
&=\int_{0}^{\pi}(u_{xx}+u^{3})\sin{x}\dx\\
&=
\end{align*}
\end{document}

>>>>

\subsection{Analysis of the Initial Conditions}
We begin by letting
\[
F(t)=\int_{0}^{\pi}u(x,t)\sin{x}\dx.
\]
Differentiating with respect to $t$ yields
\begin{align*}
F'(t)&=\int_{0}^{\pi}u_{t}\sin{x}\dx\\
&=\int_{0}^{\pi}(u_{xx}+u^{3})\sin{x}\dx
\end{align*}
Integrating leaves us with
\begin{equation}\label{fprime}
F'(t)=-F(t)+\int_{0}^{\pi}u^{3}\sin{x}\dx.
\end{equation}

We now want to determine bound on $F(t)$. Recall H\"older's inequality when concerned with the
Lebesgue measure:
\[
\int_{D}|f(x)g(x)|\dx\leq
\left(\int_{D}|f(x)|^{p}\dx\right)^{1\over p}
\left(\int_{D}|g(x)|^{q}\dx\right)^{1\over q}
\]
where $1/p + 1/q=1$. Letting $p=3$ and $q=3/2$, we have
\begin{align*}
F(t)&=\int_{0}^{\pi}\sin^{1/3}{(x)}u\sin^{2/3}{(x)}\dx\\
&\leq
\left(\int_{0}^{\pi}(\sin^{2/3}{x})^{3/2}\dx\right)^{2/3}
\left(\int_{0}^{\pi}(u\sin^{1/3}{x})^{3}\dx\right)^{1/3}\\
&=\left(\int_{0}^{\pi}\sin{x}\dx\right)^{2/3}
\left(\int_{0}^{\pi}u^{3}\sin{x}\dx\right)^{1/3}\\
&= 2^{2/3}\left(\int_{0}^{\pi}u^{3}\sin{x}\dx\right)^{1/3}.
\end{align*}
Cubing both sides of the inequality yields
\begin{align*}
F^{3}(t)&\leq4\int_{0}^{\pi}u^{3}\sin{x}\dx\\
{1\over4}F^{3}(t)&\leq\int_{0}^{\pi}u^{3}\sin{x}\dx\\
\end{align*}
By \eqref{fprime}, we have that
\begin{equation}\label{fpineq}
F'(t)\geq-F(t)+{1\over4}F^{3}(t).
\end{equation}

We now need to show that the solution to \eqref{nlinh} blows up as $F(t)\to\infty$. We begin by
letting $G(t) = F^{-2}(t)$. Then
\begin{align*}
G'(t)&=-2F^{-1}(t)F'(t)\\
-{1\over2}G'(t)F(t)&=F'(t).
\end{align*}
We can substitute this into the inequality in \eqref{fpineq}.
\begin{align*}
-{1\over2}G'(t)F(t)&\geq-F(t)+{1\over4}F^{3}(t)\\
G'(t)&\leq2-{1\over2}F^{2}(t)\\
G'(t)&\leq2-{1\over2G(t)} %% TODO -- fix this :(
\end{align*}
Solving this differential inequality for $G(t)$ yields
\[
G(t)\leq{1\over4}+\left(G(0)-{1\over4}\right)e^{2t}.
\]
Back substituting $G(t)=F^{-2}(t)$ gives us
\begin{align}
F^{-2}(t)&\leq{1\over4}+\left({1\over F^{2}(0)}-{1\over4}\right)e^{2t}\\
F(t)&\geq\left[{1\over4}+\left({1\over F^{2}(0)}-{1\over4}\right)e^{2t}\right]^{-1/2}\label{final_ineq}.
\end{align}

\end{document}

### 2016-08-23 resume/work.tex
starting new semester

\item National Aeronautics and Space Administration (NASA) $\Bigcdot$ November 2015 - Present
\begin{itemize}
\item Developed Android applications for Google Glass, Vuzix, and Recon Jet headsets
\item Worked closely with a university professor to plan and create the application
\item Participated in laser safety training
\end{itemize}

@@

\item Christopher Newport University $\Bigcdot$ September 2013 - Present
\begin{itemize}
\item IT Customer Service Representative
\begin{itemize}
\item Aided customers with various software related IT issues
\item Assisted technicians with tasks such as installing hardware
\end{itemize}
\item Tutor for the Center for Academic Success
\begin{itemize}
\item Tutored several subjects including Mathematics (mostly Calculus), Computer Engineering, and
Computer Science
\item Participated in both one on one tutoring and group tutoring
\item Created various resources for other Calculus tutors to use
\end{itemize}
\end{itemize}

>>>>

\item National Aeronautics and Space Administration (NASA) $\Bigcdot$ November 2015 - Present
\begin{itemize}
\item Developed Android applications for Google Glass, Vuzix M100, and Recon Jet headsets
\item Worked closely with a university professor to plan and create the application
\item Participated in laser safety training and received laser operator certification

\end{itemize}

@@

\item Christopher Newport University $\Bigcdot$ September 2013 - Present
\begin{itemize}
\item Tutor for the Center for Academic Success (Fall 2015 - Present)
\begin{itemize}
\item Tutored several subjects including Mathematics (mostly Calculus), Computer Engineering, and
Computer Science
\item Participated in both one on one tutoring and group tutoring
\item Created various resources for other Calculus tutors to use
\end{itemize}
\item IT Customer Service Representative (Fall 2014 - Spring 2016)
\begin{itemize}
\item Aided customers with various software related IT issues
\item Assisted technicians with tasks such as installing hardware
\end{itemize}
\end{itemize}
